Smart Drill-Down

### 2014-11-29 TableSummarization/Paper/algorithms.tex
small changes

\begin{comment}
However, we can make the problem convex (and hence tractable) with two simplifications. The first simplification is, we modify our objective function to use hinge-loss instead of a step function. That is, our new objective function to maximise is $$\sum_{r^{\prime} \in L} p_{r^{\prime}}\textrm{min}(1, \frac{ess(r^{\prime})}{minSS} $$
Here we assume that it is acceptable to run our algorithm on samples smaller than $minSS$,  though we still prefer bigger sample sizes upto $minSS$. The other simplification we make is assuming that the sample sizes $n_r$ are real numbers instead of integers. After obtaining our optimal sample sizes, we can round them up to get integer sample sizes. This will increase the memory usage by at most $|U|$, the number of nodes in displayed tree. $|U|$ is usually negligible compared to the memory capacity, or $minSS$.

@@

The main weakness of this approach is that the hinge-loss objective rewards values of $ess < minSS$, which may lead us to all leaves having large $ess$ values that are nonetheless less than $minSS$, and thus 
\end{comment}

>>>>

-----Hinge-loss begin-----

However, we can make the problem convex (and hence tractable) with two simplifications. The first simplification is, we modify our objective function to use hinge-loss instead of a step function. That is, our new objective function to maximise is $$\sum_{r^{\prime} \in L} p_{r^{\prime}}\textrm{min}(1, \frac{ess(r^{\prime})}{minSS} $$
Here we assume that it is acceptable to run our algorithm on samples smaller than $minSS$,  though we still prefer bigger sample sizes upto $minSS$. The other simplification we make is assuming that the sample sizes $n_r$ are real numbers instead of integers. After obtaining our optimal sample sizes, we can round them up to get integer sample sizes. This will increase the memory usage by at most $|U|$, the number of nodes in displayed tree. $|U|$ is usually negligible compared to the memory capacity, or $minSS$.

@@

The main weakness of this approach is that the hinge-loss objective rewards values of $ess < minSS$, which may lead us to all leaves having large $ess$ values that are nonetheless less than $minSS$, and thus gives lower quality count estimates than required by the user.

----Hinge-loss-end-----
